Global optimization: from one-dimensional to multidimensional problems via the dimensionality reduction

### 2017-10-31 2017/ParOptBook/Chapter1.tex
References and some misprints are corrected

The detailed consideration and justification of the algorithms based on the nested optimization scheme and on the dimensionality reduction schemes using Peano-type curves can be found, for example, in this monograph (see \cite{1_BarGerStrChap6, 1_GriIsrChap5}). 
% 
\begin{thebibliography}{99.}
\bibitem{1_BarGerStrChap4} Barkalov, K.A., Gergel, V.P., Strongin, R.G.: Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints. This volume.
\bibitem{1_BarGerStrChap6} Barkalov, K.A., Gergel, V.P., Strongin, R.G.: Parallel computations for the multidimensional multiextremal optimization problems with the dimensionality reduction using Peano curves. This volume.
\bibitem{1_BetroSchoen} Betro, B., Schoen, F.: Sequential stopping rules for the multistart algorithm in global optimisation. Math. Program. \textbf{38}(3), 271--286 (1987)
\bibitem{1_BoendeRinnooy}	Boender, C.G.E, Rinnooy Kan, A.H.G.: Bayesian stopping rules for multistart global optimization methods. Math. Program. \textbf{37}(1), 59--80 (1987)
\bibitem{1_Butz}	Butz, A.R. Space-Filling Curves and Mathematical Programming.: Inform. Control \textbf{12}, 314--330 (1968)
\bibitem{1_CarrHowe}	Carr, C.R., Howe, C.W.: Quantitative Decision Procedures in Management and Economic: Deterministic Theory and Applications. McGraw-Hill, New York (1964)
\bibitem{1_Evtushenko}	Evtushenko, Yu.G.: Numerical Optimization Techniques. Translation Series in Mathematics and Engineering. Optimization Software  Inc., Publication Division, New York (1985)
\bibitem{1_FloudasPardalos} Floudas, C.A., Pardalos, P.M.: State of the Art in Global Optimization. Kluwer Academic Publishers, Dordrecht (1996)
\bibitem{1_GerGriIsr} Gergel, V.,  Grishagin, V., Israfilov, R.: Local tuning in nested scheme of global optimization, Procedia Computer Science \textbf{51}, 865--874 (2015) 
\bibitem{1_GerGriGer}	Gergel, V., Grishagin, V., Gergel, A.: Adaptive nested optimization scheme for multidimensional global search, J. Glob. Opt. \textbf{66}, 35–51 (2016).
\bibitem{1_Goertzel}	Goertzel, B.: Global Optimization with Space-Filling Curves. Appl. Math. Lett. 12, 133--135 (1999)
\bibitem{1_GriIsrChap5}Grishagin, V.A., Israfilov, R.A.: Sequential and parallel algorithms for multidimensional multiextremal optimization based on the nested scheme of dimensionality
reduction. This volume.
\bibitem{1_GriIsrAIP}	Grishagin, V.A., Israfilov, R.A.: Global search acceleration in the nested optimization scheme. AIP Conf. Proc. \textbf{1738}, 400010 (2016)
\bibitem{1_GriIsrSerg}	Grishagin, V.,  Israfilov, R., Sergeyev, Y.: Convergence conditions and numerical comparison of global optimization methods based on dimensionality reduction schemes. Appl. Math.  Comput. (2017) doi:10.1016/j.amc.2017.06.036

>>>>

The detailed consideration and justification of the algorithms based on the nested optimization scheme and on the dimensionality reduction schemes using Peano-type curves can be found, for example, in this monograph (see \cite{1_BarGerStrChap6, 1_GriIsrChap5}). 
% 
\begin{thebibliography}{99.}
\bibitem{1_BarGerStrChap4} Barkalov, K.A., Gergel, V.P., Strongin, R.G.: Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints. This volume.
\bibitem{1_BarGerStrChap6} Barkalov, K.A., Gergel, V.P., Strongin, R.G.: Parallel computations for the multidimensional multiextremal optimization problems with the dimensionality reduction using Peano curves. This volume.
\bibitem{1_BetroSchoen} Betro, B., Schoen, F.: Sequential stopping rules for the multistart algorithm in global optimisation. Math. Program. \textbf{38}(3), 271--286 (1987)
\bibitem{1_BoendeRinnooy}	Boender, C.G.E, Rinnooy Kan, A.H.G.: Bayesian stopping rules for multistart global optimization methods. Math. Program. \textbf{37}(1), 59--80 (1987)
\bibitem{1_Butz}	Butz, A.R. Space-Filling Curves and Mathematical Programming.: Inform. Control \textbf{12}, 314--330 (1968)
\bibitem{1_CarrHowe}	Carr, C.R., Howe, C.W.: Quantitative Decision Procedures in Management and Economic: Deterministic Theory and Applications. McGraw-Hill, New York (1964)
\bibitem{1_Evtushenko}	Evtushenko, Yu.G.: Numerical Optimization Techniques. Translation Series in Mathematics and Engineering. Optimization Software  Inc., Publication Division, New York (1985)
\bibitem{1_FloudasPardalos} Floudas, C.A., Pardalos, P.M.: State of the Art in Global Optimization. Kluwer Academic Publishers, Dordrecht (1996)
\bibitem{1_GerGriIsr} Gergel, V.,  Grishagin, V., Israfilov, R.: Local tuning in nested scheme of global optimization, Procedia Computer Science \textbf{51}, 865--874 (2015) 
\bibitem{1_GerGriGer}	Gergel, V., Grishagin, V., Gergel, A.: Adaptive nested optimization scheme for multidimensional global search, J. Glob. Opt. \textbf{66}, 35–51 (2016).
\bibitem{1_Goertzel}	Goertzel, B.: Global Optimization with Space-Filling Curves. Appl. Math. Lett. 12, 133--135 (1999)
\bibitem{1_GriIsrChap5}Grishagin, V.A., Israfilov, R.A.: Sequential and parallel algorithms for multidimensional multiextremal optimization based on the nested scheme of dimensionality
reduction. This volume.
\bibitem{1_GriIsrAIP}	Grishagin, V.A., Israfilov, R.A.: Global search acceleration in the nested optimization scheme. AIP Conf. Proc. \textbf{1738}, 400010 (2016)
\bibitem{1_GriIsrSerg}	
Grishagin, V.,  Israfilov, R., Sergeyev, Y.: Convergence conditions and numerical comparison of global optimization methods based on dimensionality reduction schemes. Appl. Math.  Comput. \textbf{318}, 270--280 (2018)
